\documentclass[]{article}
\usepackage[margin=0.5in]{geometry}

%opening
\title{POSimple Software Porposal}
\author{Adam Beech, Gray Meeks, Luke Nutt, and Russ Seaman}

\begin{document}

\maketitle

\begin{abstract}
	POSimple is an easy to use, intuitive point of sale software solution. The goal of POSimple is to provide businesses of any size with the tools they need to manage customers, inventory, and transactions with optimal efficiency.

\end{abstract}

\section{Functionality for POSimple:}
	\begin{enumerate}
		\item Customer management:
		\begin{itemize}
			\item View, add, delete, and edit customers.
			\item Access historical reports based on customer’s purchase history.
		\end{itemize}
		\item Inventory management:
		\begin{itemize}
			\item View, add delete, and edit products.
			\item Keep track of inventory in real-time.
		\end{itemize}
		\item Transaction management:
		\begin{itemize}
			\item Process new orders.
			\item Manage current orders.
			\item View previously fulfilled orders.
		\end{itemize}
		\item Sales Reporting
		\begin{itemize}
			\item See which products perform best based on both sale margin and volume.
			\item View historical sales data based on a given time frame.
		\end{itemize}
		\item Employee permissions:
		\begin{itemize}
			\item High level employees can be given all-access to data permissions allowing them to edit, and delete.
			\item Low level employees can be given limited access to data permissions allowing them to view data but not add, edit, or delete anything.
		\end{itemize}
	\end{enumerate}

\end{document}
